---
title: "bonusLab-vignette"
output: rmarkdown::html_vignette
author: Marc Braun
vignette: >
  %\VignetteIndexEntry{bonusLab-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

```

## Setup
To install the bonusLab package, source it from GitHub with the command `devtools::install_github("Marbr987/bonus_lab")`.
Then load the bonusLab package and the packages and data required for this vignette.
```{r}
library(bonusLab)
library(mlbench)
library(caret)
data("BostonHousing")
```

## 1. Train Test Split
First of all, the BostonHousing dataset is divided in a train and a test set.

```{r}
train_indices <- createDataPartition(BostonHousing[,1], p=0.8)[[1]]
BostonHousing_train <- BostonHousing[train_indices,]
BostonHousing_test <- BostonHousing[-train_indices,]
```

## 2. Fit a linear regression model and a fit a linear regression model with forward selection of covariates on the training dataset
Some Description
```{r}
# The code
```

## 3. Evaluate the performance of this model on the training dataset
Some Description
```{r}
# The code
```

## 4. Fit a ridge regression model using ridgereg() function
Some Description
```{r}
# The code
```

## 5. Find the best hyperparameter value for λ
Some Description
```{r}
# The code
```

## 6. Evaluate the performance of all three models
Some Description
```{r}
# The code
```




